Title of the document here

### 2015-01-26 rmtw/assignment_1/assignment_1.tex
Changes to assignment_1, started notes on methodology

Both industry and academia face the problem of maintainability. As stated previously, many times the readability of code affects the codes maintainability. This study could help some in industry to pick languages for certain tasks for maintainability reasons alone. Further studies could be conducted by to determine if there is a correlation between the popularity of projects and the readability of their languages. Furthermore, academia would be interested in which languages are more popular and useful for learning. By further investigating the design of the programming languages themselves, future languages which are developed could build upon the success of those which came before them.
\newline
The purpose of this survey study is therefore to test what are the differences in readability between five common and well known programming languages. With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
\newline

The Independent variables will be defined as the experience, age, preferred language, least preferred language and the working language of the participant. The dependent variable in this example will be the readability of the language.
\newline

@@

* Describe  and explain the research  strategy (i.e.  Survey/Questionnaire)
and investigation methods that  will  be  used  for the study.  Motivate  your  
choice  of  survey/questionnaire  using relevant  references.
* Describe  data  collection  procedures, sampling  method(s),  number  of  
subjects, response  rate  etc.
* Create  questions for your  survey  (include  the questions in  your  report)
* Describe  the population  and size  of  population
* Describe  and motive  method  for analyzing the data
* Discuss validity  threats

>>>>

Both industry and academia face the problem of maintainability. As stated previously, many times the readability of code affects the codes maintainability. This study could help some in industry to pick languages for certain tasks for maintainability reasons alone. Further studies could be conducted by to determine if there is a correlation between the popularity of projects and the readability of their languages. Furthermore, academia would be interested in which languages are more popular and useful for learning. By further investigating the design of the programming languages themselves, future languages which are developed could build upon the success of those which came before them.
\newline
The purpose of this survey study is therefore to find what are the differences in readability between five common and well known programming languages. With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
\newline

The Independent variables will be defined as the experience, occupation, preferred language, least preferred language and the working language of the participant. The dependent variable in this example will be the readability of the language.
\newline

@@

* Describe  and explain the research  strategy (i.e.  Survey/Questionnaire)
and investigation methods that  will  be  used  for the study.  Motivate  your  
choice  of  survey/questionnaire  using relevant  references.

The main purpose of our study is to discover differences between the perceived readability of code. To discover an answer to this question, we would likely collect data and opinions from a broad population. As such, we most likely need to perform a research survey. This is reinforced by Easterbrook et. al \cite{easterbrook2008selecting} who stated ``Survey research is used to identify the characteristics of a broad population of individuals''.

 case-control design - ``asks each participant about several related issues in 
order to establish whether a correlation exists between them,'' \cite{easterbrook2008selecting}

We will use a survey/questionnaire to collect the data.
Sampling - ID a small subset of the entire population

* Describe  data  collection  procedures, sampling  method(s),  number  of  
subjects, response  rate  etc.

Random sampling from 200 people(guess). Sample 10\%, collect online via survey, Response rate of 15/20 (75\%)

Sampling bias - What we might face, how we overcome. State which threats and how they were minimised

* Create  questions for your  survey  (include  the questions in  your  report)
%Table goes here
* Describe  the population  and size  of  population

The population will be software developers in the SEM program. This includes teachers, students, professionals and hobbyists. Lets say the sample is 20 persons from the whole of SEM, 1st, 2nd, 3rd and staff.

\cite{easterbrook2008selecting} - ``A major challenge in survey research is to control for sampling bias'' \& `` the respondents to 
the survey may not be representative of the target population. ''

* Describe  and motive  method  for analyzing the data

* Discuss validity  threats
  Sampling Bias ?
